Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-13 Manuscript.Rmd
Some daily correlations are negative due to the simplicity of the DMN-pairing heuristic. This affects Corr vs FV even if the maps look great across days. I added code to identify individuals with negative cross-day correlations to examine later.

>>>>

# Some participants have strongly uncorrelated maps because 7m isn't fully covered on one of the days
# ARI doesn't mind this, so the results are fine
# But the Corr vs FV analysis below is badly affected
# For now I'm just selecting the individuals that have negatively correlated FVectors
# It might be worth visually inspecting each to see if a simple heuristic works (i.e. if corr < -0.5, then FV * -1 & 1 - FB)
# Although this doesn't adress which half is the culprit
unCorrParticipants <- data.frame(SubjID = subjList,
                                 Corrs = sapply(seq(1, nSubj *2, by = 2), function(x) {cor(Summaries_halves_unthresh[[x]]$FiedlerVec, Summaries_halves_unthresh[[x+1]]$FiedlerVec)})) %>%
  filter(Corrs < 0)
